\documentclass[a4paper,10pt]{article}
\usepackage{latexsym}
\usepackage{marvosym}
\usepackage[empty]{fullpage} % optional, based on preference
\usepackage{titlesec}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}

%----------FONT & SPACING----------
\usepackage{palatino}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\setlength{\tabcolsep}{0in}
\addtolength{\oddsidemargin}{-0.25in}
\addtolength{\evensidemargin}{-0.25in}
\addtolength{\textwidth}{0.5in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

%----------SECTION FORMATTING----------
\titleformat{\section}[block]{\scshape\raggedright\large}{\thesection}{1em}{\vspace{-2pt}}[\titlerule \vspace{-5pt}]
%----------RESUME START----------
\begin{document}

\centerline{\huge \bf Francisco Vu}
\centerline{Milton, MA \ $|$ \ (617) 898-7325}
\centerline{\href{mailto:franvu225@gmail.com}{franvu225@gmail.com} \ $|$ \ \href{https://github.com/franware1}{github.com/franware1} \ $|$ \ \href{https://linkedin.com/franvu225}{linkedin.com/franvu225}}

\section*{Education}

\textbf{University of Massachusetts Boston} \hfill Boston, MA \\
\textit{Bachelor of Science in Computer Science} \hfill \textit{Expected May 2026} \\
Relevant Courses: Data Structures, Algorithms, Databases, Machine Learning, Game Development

\section*{Technical Skills}
\textbf{Languages:} Java, C, Python, C\#, SQL \\
\textbf{Tools \& Frameworks:} Unity, Git, SQLite, Tailwind \\
\textbf{Concepts:} Data Structures, OOP, Database Management, Machine Learning

\section*{Projects}

\noindent\textbf{Portfolio Website (In Progress)} \hfill \textit{HTML, CSS, JavaScript, Tailwind}
\vspace{-5pt}
\begin{itemize}[leftmargin=1.5em, label={-}]
    \item Developed a fully responsive, modern portfolio website using Tailwind CSS, HTML, CSS, and JavaScript, showcasing strong front-end development skills.
    \item Focused on building a seamless, intuitive user interface (UI) while improving my understanding of UI/UX principles.
    \item Gained hands-on experience with version control and Git while managing the project's codebase.
\end{itemize}

\noindent\textbf{Machine Learning Song Success Classifier (In Progress)} \hfill \textit{Octave, SQLite} \\
\vspace{-10pt}
\begin{itemize}[leftmargin=1.5em, label={-}]
  \item Collected and preprocessed song data using SQLite databases, ensuring data integrity and efficient querying for analysis.
  \item Built logistic regression and support vector machine (SVM) models in Octave to predict song success.
  \item Analyzed audio features and metadata to uncover patterns in popular music, enhancing model performance with feature selection.
\end{itemize}

\noindent\textbf{3D Unity Game (In Progress)} \hfill \textit{C\#, Unity} \\
\vspace{-10pt}
\begin{itemize}[leftmargin=1.5em, label={-}]
  \item Developing a 3D game environment using Unity and scripting with C\#.
  \item Designing player mechanics, physics interactions, basic enemy AI, and game UI.
\end{itemize}

\noindent\textbf{CryptoCoin Bot} \hfill \textit{Python} \\
\vspace{-10pt}
\begin{itemize}[leftmargin=1.5em, label={-}]
  \item Created an automated Telegram messaging robot to notify users about trending and potentially lucrative Crypto investment opportunities.
  \item Implemented key data structures (e.g., linked lists, trees, hash maps) in Python to analyze Cryptocoin market trends.
  \item Focused on optimizing time and space complexity for performance-critical applications.
\end{itemize}

%------- Job History -------%

\section*{Experience (Job History)}

\noindent\textbf{Personal Care Aide (PCA)} \hfill \textit{October 2018 - October 2020} \\
\textit{Tempus Unlimited} \hfill \textit{Stoughton, MA} \\
\vspace{-5pt}
\begin{itemize}[leftmargin=0.15in, label={-}]
  \item Worked directly with patient and tended to physical, emotional, and medical demands.
  \item Developed emotional intelligence working with autistic patient and understanding of the developmental disability.
\end{itemize}

\noindent\textbf{Cashier/Customer Service} \hfill \textit{November 2023 - July 2024} \\
\textit{Seasons Corner Market} \hfill \textit{Norwood, MA} \\
\vspace{-10pt}
\begin{itemize}[leftmargin=0.15in, label={-}]
  \item Developed interpersonal communication skills during tenure.
  \item Helped the customers with technical issues regarding the Rewards program and banking issues that might arise during gas payment
  \item Became familiar with Seasons sales POS.
\end{itemize}

\end{document}
